\documentclass{article}

\title{Kyle Onela's Resume}
\author{Kyle Onela}

\usepackage[letterpaper, margin=0.5in]{geometry}
\setlength\parindent{0pt}

\usepackage{titlesec}
\titleformat{\section} {\normalfont\large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\pagenumbering{gobble} % disable page numbering
\usepackage[none]{hyphenat}

\usepackage{subfiles}

\begin{document}
\centerline{\LARGE\textbf{Kyle Onela}}
\smallskip
\centerline{
  \textbf{(616) 368-7460 \texttt{|}} \
  \textbf{kyleonela@gmail.com \texttt{|}} \
  \textbf{linkedin.com/in/kyleonela \texttt{|}} \
  \textbf{github.com/kyleonela}}

\section*{Work Experience}
\textbf{Senior Software Engineer} \hfill \textbf{September 2021 --- April 2025}\\
\textit{Initech Global, Grand Rapids, MI}
\begin{itemize}
  \item Designed and modernized internal applications like Quality and Air Freight using Next.js (React) and AWS at Bissell. Engaged with end users to gather feedback, enhance functionality, and improve the overall user experience. 
  Implemented CI/CD pipelines using GitHub Actions and Azure DevOps (ADO) for build and release management.
  \item Partnered with the Creators Backend for Frontend (BFF) team at Amway to develop scalable AWS serverless cloud infrastructure, ensuring functional feasibility with design and product teams. Delivered microservices-based backend APIs to support Creators+ application enhancements utilizing GraphQL, Node.js (TypeScript), AWS, and Jest with CI/CD pipelines for automated deployment and testing.
  \item Delivered microservices on AWS using DynamoDB, Lambda (Node.js), API Gateway, and CDK as part of the 360 Messaging team at Amway, enabling scalable, event-driven backend services. Built an Angular app to manage user and ABO preferences, improving CRM efficiency.
  % \item Developed event-driven microservices with AWS Lambda, API Gateway, DynamoDB, and CDK at Amway with the 360 Messaging team. Built an Angular application to manage ABO preferences and improve CRM workflows.
  \item Mentored interns and junior software developers and assisted HR in recruiting and interviewing candidates weekly.
\end{itemize}
\medskip

\textbf{Software Engineer} \hfill \textbf{November 2020 --- August 2021}\\
\textit{Initech Global, Grand Rapids, MI}
\begin{itemize}
  \item Assisted the APES team at Amway in developing an Angular application to automate exception payment processing in the North America financing system, including exception scheduling, payment calculations, and invoice record creation.
  \ifdefined\includeanalytics
    \item Supported the Experience Optimization and Personalization Enablement team at Amway to enhance user experience across e-commerce sites by leveraging Optimizely and Qualtrics for A/B testing and personalization strategies.
  \fi
  \item Co-led the Initech Web Design team in redesigning and expanding content for the official company website, enhancing user experience, brand consistency, and overall site engagement.
  \item Enhanced CRM performance at Design Force Marketing by optimizing the application and refactoring legacy code using Angular, C\#, and ASP.NET Core MVC, resulting in improved speed, efficiency, and maintainability.
\end{itemize}
\medskip

\textbf{Associate Software Engineer} \hfill \textbf{May 2020 --- November 2020}\\
\textit{Initech Global, Grand Rapids, MI}
\begin{itemize}
  \ifdefined\includeanalytics
    \item Optimized and maintained Amway’s Tealium ecosystem to ensure data integrity, supporting the successful launch of Heap Analytics across all Amway e-commerce platforms.
  \fi
  \item Designed and implemented MyInitech, a scalable, cloud-based workforce management system that streamlines HR and project management operations, leveraging Angular for the front end and Spring Boot with MySQL for the back end. Enhanced and extended existing RESTful APIs to support new features and improve system performance, and wrote unit tests with JUnit and Mockito to ensure backend reliability.
\end{itemize}
\medskip

\textbf{Software Development Intern} \hfill \textbf{May 2019 --- May 2020}\\
\textit{Initech Global, Grand Rapids, MI}
\begin{itemize}
  \item Developed a fully functional Homeowner's Association (HOA) web application using Angular, Spring Boot, and MySQL to build a robust system featuring RESTful APIs, efficient CRUD operations, seamless user authentication, and responsive UI components. Wrote unit tests with JUnit and Mockito to validate core backend functionality.
\end{itemize}

\section*{Education}
\textbf{Bachelor of Science in Computer Science} \hfill \textbf{August 2016 --- May 2020}\\
\textit{Grand Valley State University, Allendale, MI}
\section*{Skills}
\textbf{Programming Languages}: Java, TypeScript, JavaScript, C\#, Python \\
\textbf{Web Development}: Angular, Spring Boot, React, Node.js, Next.js, ASP.NET Core MVC, HTML, CSS\\
\textbf{Other}: Git (GitHub, BitBucket), SQL (MySQL, PostgreSQL), Amazon Web Services (AWS), Jira, Azure DevOps (ADO), Jest, Docker, Jenkins, GraphQL, Agile (Scrum, Kanban), Swagger, Postman, Microsoft Office 365

\section*{Certifications}
AWS Certified Cloud Practitioner \hfill \textbf{June 2021 --- June 2024}

\end{document}